Regularized target encoding outperforms traditional methods in supervised machine learning with high cardinality features

### 2021-09-08 publication/manuscript.Rmd
add optimal scaling references to manuscript and bib

In our study, several decisions were necessary to make answering our research questions technically and computationally feasible.
First, we only used minimal tuning for our ML algorithms, as we were not interested in comparing their performance against each other.
This probably led to suboptimal performance for the GB, KNN, and SVM learners.
When interpreting our results, we assume that the encoder rankings are comparable when more extensive tuning is used.
This seems plausible, considering the high stability of our meta rankings between algorithms.
We only use 5-fold-CV without repetitions to estimate predictive performance, but due to a small variance between folds, we could confidently detect performance differences of encoders for many datasets.
As we are interested in model-agnostic methods that can be combined with any supervised ML algorithm, we do not investigate several strategies proposed in the recent literature [@guo_2016; @prokhorenkova_2018].
Additionally, we only investigate univariate encodings, i.e. we always encode each variable separately.
Levels with comparable main effects can therefore not be distinguished based on the transformed feature, which prevents the consecutive ML algorithm from learning interactions for specific levels.
Methods that can jointly encode several variables and therefore leverage correlation structures between the different variables are an interesting avenue of research in the future. Another interesting avenue is using target-based encoding strategies to learn a vector-valued representation of a level, similar to entity embeddings [@guo_2016].
We furthermore only investigate traditional categorical variables and do not extend our analysis to multi-categorical variables or text-strings [@cerda_2018; @cerda_2020], where other encoding techniques can harvest additional information.

>>>>

In our study, several decisions were necessary to make answering our research questions technically and computationally feasible.
First, we only used minimal tuning for our ML algorithms, as we were not interested in comparing their performance against each other.
This probably led to suboptimal performance for the GB, KNN, and SVM learners.
When interpreting our results, we assume that the encoder rankings are comparable when more extensive tuning is used.
This seems plausible, considering the high stability of our meta rankings between algorithms.
We only use 5-fold-CV without repetitions to estimate predictive performance, but due to a small variance between folds, we could confidently detect performance differences of encoders for many datasets.
As we are interested in model-agnostic methods that can be combined with any supervised ML algorithm, we do not investigate several strategies proposed in the recent literature [@guo_2016; @prokhorenkova_2018].
Additionally, we only investigate univariate encodings, i.e. we always encode each variable separately.
Levels with comparable main effects can therefore not be distinguished based on the transformed feature, which prevents the consecutive ML algorithm from learning interactions for specific levels.
Methods that can jointly encode several variables and therefore leverage correlation structures between the different variables are an interesting avenue of research in the future:
Recent approaches use target-based encoding strategies to learn a vector-valued representation of a level, similar to entity embeddings [@guo_2016].
Those should be compared to classical approaches from the optimal scaling literature [e.g. @deleeuw_1976] leading to the *aspect* framework [@mair_2010], which is unfortunately unfamiliar to many ML researchers.
We furthermore only investigate traditional categorical variables and do not extend our analysis to multi-categorical variables or text-strings [@cerda_2018; @cerda_2020], where other encoding techniques can harvest additional information.
